---
title: "ishratc_OriginalHomeworkCode_03"
author: "Ishrat Chowdhury"
date: "October 3, 2019"
output: html_document
---

Problems:

1. The last question is my biggest issue, I am having trouble extracting out 99 samples. I know I made a list off 99 but I have no idea of hey are 30 rows each, in addition the list of 99 looks different form the orginal table. I feel like once I get that 
2. I also had trouble understanding why the two non-normally distributed variables would have different code for finding CI.
3. Suggestions for showing that height and weight are in fact related? I have a regression line now and was thinking about putting a R^2 value
4. Any idea why I had to load my data in twice and why the firts one was not working with {ggplot} it has soemthing to do with how it was recognizing the variables. I don't think it was recongizing them as factors. 
5. Gnerall ways to make ti prettier? There are long chunks of R code, should I break them uo more.

Gosh this homework was hard thanks for all the help!


First let's load our data into R

```{r}
library(curl)
f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN597_Fall19/zombies.csv")
d <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
head(d)
```

1. Calculate the population mean and standard deviation for each quantitative random variable.

```{r}
height<-d$height
hm<-mean(height)
hm
hsd<-sd(height)
hsd

weight<-d$weight
wm<-mean(weight)
wm
wsd<-sd(weight)
wsd

age<-d$age
am<-mean(age)
am
asd<-sd(age)
asd

zombies_killed<-d$zombies_killed
zm<-mean(zombies_killed)
zm
zsd<-sd(zombies_killed)
zsd

yrs_edu<-d$years_of_education
ym<-mean(yrs_edu)
ym
ysd<-sd(yrs_edu)
ysd

```
2. Use {ggplot} to make boxplots of each of these variables by gender.

So at first I didn't use {ggplot} because I wasn't paying attention but I ended up keeping this for refernce and comparison. Both look the same as they should!

```{r}
mh<- d$height[d$gender == "Male"]
fh<- d$height[d$gender == "Female"]
mw<- d$weight[d$gender == "Male"]
fw<- d$weight[d$gender == "Female"]
ma<- d$age[d$gender == "Male"]
fa<- d$age[d$gender == "Female"]
mz<- d$zombies_killed[d$gender == "Male"]
fz<- d$zombies_killed[d$gender == "Female"]
my<- yrs_edu[d$gender == "Male"]
fy<- yrs_edu[d$gender == "Female"]
par(mfrow =c(1,2))
boxplot(mh, main = "Height", xlab = "Males", ylab = "inches")
boxplot(fh, main = "Height", xlab = "Females", ylab = "inches")
boxplot(mw, main = "Weight", xlab = "Males", ylab = "pounds")
boxplot(fw, main = "Weight", xlab = "Females", ylab = "pounds")
boxplot(ma, main = "Age", xlab = "Males", ylab = "years")
boxplot(fa, main = "Age", xlab = "Females", ylab = "years")
boxplot(mz, main = "# of Zombies Killed", xlab = "Males")
boxplot(fz, main = "# of Zombies Killed", xlab = "Females")
boxplot(my, main = "Years of Education", xlab = "Males", ylab = "years")
boxplot(fy, main = "Years of Education", xlab = "Females", ylab = "years")
```

Now to answer the question correctly

I ended up reloading the data with {readr}, because for some reason i couldnt use {ggplot} with {curl}
```{r}
library(ggplot2)
library(readr)
d1_url<-"https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN597_Fall19/zombies.csv"
d1<-read_csv(d1_url)
head(d1)
```

Height Boxplot

```{r}
h <- ggplot(d1) +
      geom_boxplot(aes(x=gender, y=height))
h
```

The rest of the boxplots follow:

```{r}
w <- ggplot(d1) +
      geom_boxplot(aes(x=gender, y=weight))
w
```

```{r}
a <- ggplot(d1) +
      geom_boxplot(aes(x=gender, y=age))
a
```

```{r}
z <- ggplot(d1) +
      geom_boxplot(aes(x=gender, y=zombies_killed))
z
```

```{r}
y <- ggplot(d1) +
      geom_boxplot(aes(x=gender, y=years_of_education))
y
```

3. Use {ggplot} to make scatterplots of height and weight in relation to age. Are these variables related? Why?

there certainly is a correlation, I have my scatterplot now, but plan on running a correlation test maybe showing an R square value or soemthing. 

```{r}
hw<-ggplot(d1, aes(x = weight, y = height)) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red")
hw
```
4. Using histograms and Q-Q plots, check whether the quantitative variables seem to be drawn from a normal distribution. Which seem to be and which do not (hint: not all are drawn from the normal distribution)? For those that are not normal, can you determine from which common distribution they are drawn?

Histograms and q-q plots for each are below. Zombies killes and years of education do not show a normal distribtuion. 

```{r}
hist(height)
qqnorm(height)
```

```{r}
hist(weight)
qqnorm(weight)
```

```{r}
hist(age)
qqnorm(age)
```

```{r}
hist(zombies_killed)
qqnorm(zombies_killed)
```


```{r}
hist(yrs_edu)
qqnorm(yrs_edu)
```

fix ones that are not normally distributed (zombies killed and yrs of edu) both appear to be right skewed

these are probably poisson because they are integers and idnependantly related 

```{r}
?dpois # dpois gives log density and ppois gives log distribution
zd<-dpois(0:12, lambda = zm)
barplot(zd)
#looks better but there is an outlier (afraid to remove points) also can I transform them 

```

```{r}
yd<-dpois(yrs_edu, lambda = ym)
yd
hist(yd)

yd<-dpois(x=0:10, lambda = ym)
barplot(yd)

```

I made barplots with the lambda (just the mean right?) This looks more normal, but I am not sure if these barplots are represetnativ eof the data or they are just ideal barplots?

5. Now use the sample() function to sample ONE subset of 30 zombie survivors (without replacement) from this population and calculate the mean and sample standard deviation for each variable. Also estimate the standard error for each variable, and construct the 95% confidence interval for each mean. Note that for the variables that are not drawn from the normal distribution, you may need to base your estimate of the CIs on slightly different code than for the normal.


This is how I subsettes the sample
```{r}
?sample
nd<-d[sample(nrow(d), 30),]
nd
str(nd)
```

mean and standard deviations of samples

```{r}
nheight<-nd$height
nhm<-mean(nheight)
nhm
nhsd<-sd(nheight)
nhsd

nweight<-nd$weight
nwm<-mean(nweight)
nwm
nwsd<-sd(nweight)
nwsd

nage<-nd$age
nam<-mean(nage)
nam
nasd<-sd(nage)
nasd

nzombies_killed<-nd$zombies_killed
nzm<-mean(nzombies_killed)
nzm
nzsd<-sd(nzombies_killed)
nzsd

nyrs_edu<-nd$years_of_education
nym<-mean(nyrs_edu)
nym
nysd<-sd(nyrs_edu)
nysd
```

standard errors and 95% ci

```{r}
hse<-sqrt(nhsd^2/30)
hse

wse<-sqrt(nwsd^2/30)
wse

ase<-sqrt(nasd^2/30)
ase

zse<-sqrt(nzsd^2/30)
zse

yse<-sqrt(nysd^2/30)
yse
```

these are all sample size 30 so t distrubution needs to be used, I am also not sure why the to Poisson distirbutions would have different code for the CI

```{r}
lower <- nhm - qt(1 - 0.05/2, df = 29) * hse  # (1-alpha)/2 each in the upper and lower tails of the distribution
upper <- nhm + qt(1 - 0.05/2, df = 29) * hse  # (1-alpha)/2 each in the upper and lower tails of the distribution
nhci_t <- c(lower, upper)
nhci_t

lower <- nwm - qt(1 - 0.05/2, df = 29) * wse  # (1-alpha)/2 each in the upper and lower tails of the distribution
upper <- nwm + qt(1 - 0.05/2, df = 29) * wse  # (1-alpha)/2 each in the upper and lower tails of the distribution
nwci_t <- c(lower, upper)
nwci_t

lower <- nam - qt(1 - 0.05/2, df = 29) * ase  # (1-alpha)/2 each in the upper and lower tails of the distribution
upper <- nam + qt(1 - 0.05/2, df = 29) * ase  # (1-alpha)/2 each in the upper and lower tails of the distribution
naci_t <- c(lower, upper)
naci_t


#doesn't lambda equal mean so shouldn't it be the same???

lower <- nzm - qt(1 - 0.05/2, df = 29) * zse  # (1-alpha)/2 each in the upper and lower tails of the distribution
upper <- nzm + qt(1 - 0.05/2, df = 29) * zse  # (1-alpha)/2 each in the upper and lower tails of the distribution
zwci_t <- c(lower, upper)
zwci_t

lower <- nym - qt(1 - 0.05/2, df = 29) * yse  # (1-alpha)/2 each in the upper and lower tails of the distribution
upper <- nym + qt(1 - 0.05/2, df = 29) * yse  # (1-alpha)/2 each in the upper and lower tails of the distribution
yaci_t <- c(lower, upper)
yaci_t

```

6. Now draw 99 more random samples of 30 zombie apocalypse survivors, and calculate the mean for each variable for each of these samples. Together with the first sample you drew, you now have a set of 100 means for each variable (each based on 30 observations), which constitutes a sampling distribution for each variable. What are the means and standard deviations of this distribution of means for each variable? How do the standard deviations of means compare to the standard errors estimated in [5]? What do these sampling distributions look like (a graph might help here)? Are they normally distributed? What about for those variables that you concluded were not originally drawn from a normal distribution?


** I'm really not sure about this one, I've tried multiple things. Right now all I can do is get a list off 99 elemtns but I am not sure if each elemtn has 30 rows. I know they have 10 columns though. 

```{r}
k <- 99 # number of samples
n <- 10 # size of each sample
s <- NULL # dummy variable to hold each sample
for (i in 1:k){
    s[[i]] <- sample(d1,size=n, replace=FALSE)
}
head(s)

```



```{r}
sampling<-fucntion(d, nSamples = 99, nRows, 30)

sample<-replicate(99,smaple(nrow(30), 10, replace = FALSE))

```

