---
title: "ishratc_FinalHomeworkCode_03"
author: "Ishrat Chowdhury"
date: "October 14, 2019"
output: html_document
---


First let's load our data into R

```{r}
library(curl)
f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN597_Fall19/zombies.csv")
d <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
head(d)
```

1. Calculate the population mean and standard deviation for each quantitative random variable.

```{r}
height<-d$height
hm<-mean(height)
hm
hsd<-sd(height)
hsd

weight<-d$weight
wm<-mean(weight)
wm
wsd<-sd(weight)
wsd

age<-d$age
am<-mean(age)
am
asd<-sd(age)
asd

zombies_killed<-d$zombies_killed
zm<-mean(zombies_killed)
zm
zsd<-sd(zombies_killed)
zsd

yrs_edu<-d$years_of_education
ym<-mean(yrs_edu)
ym
ysd<-sd(yrs_edu)
ysd

```
2. Use {ggplot} to make boxplots of each of these variables by gender.

I had to reload the data with {readr}, because for some reason I couldnt use {ggplot} with {curl}.

```{r}
library(ggplot2)
library(readr)
d1_url<-"https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN597_Fall19/zombies.csv"
d1<-read_csv(d1_url)
head(d1)
```

Height Boxplot

```{r}
h <- ggplot(d1) +
      geom_boxplot(aes(x=gender, y=height))
h
```

The rest of the boxplots follow:

```{r}
w <- ggplot(d1) +
      geom_boxplot(aes(x=gender, y=weight))
w
```

```{r}
a <- ggplot(d1) +
      geom_boxplot(aes(x=gender, y=age))
a
```

```{r}
z <- ggplot(d1) +
      geom_boxplot(aes(x=gender, y=zombies_killed))
z
```

```{r}
y <- ggplot(d1) +
      geom_boxplot(aes(x=gender, y=years_of_education))
y
```

3. Use {ggplot} to make scatterplots of height and weight in relation to age. Are these variables related? Why?

Revisiting the Homework after a while adn I realozed I completely misread the question. Here is an attempt to answer it correctly.

Here is the scatterplot for height and age:

```{r}
hw<-ggplot(d1, aes(x = age, y = height)) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red") 
hw + labs(title = "Height vs Age")
```

Here is the scatterplot for weight and age:

```{r}
hw<-ggplot(d1, aes(x = age, y = weight)) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red") 
hw + labs(title = "Weight vs Age")
```

Visually, it look like there is more of a relation between height and age. Now that we know more about regression models we can runa linear regression and find out.

```{r}
lmha<-lm(age ~ height, data=d1)
summary(lmha)

lmwa<-lm(age ~ weight, data=d1)
summary(lmwa)

```

The R squared for height is closer to one there for the linear relation between height and age is stronger than the relationship between weight and age.

4. Using histograms and Q-Q plots, check whether the quantitative variables seem to be drawn from a normal distribution. Which seem to be and which do not (hint: not all are drawn from the normal distribution)? For those that are not normal, can you determine from which common distribution they are drawn?

Histograms and q-q plots for each are below. Zombies killes and years of education do not show a normal distribtuion. 

```{r}
hist(height)
qqnorm(height)
```

```{r}
hist(weight)
qqnorm(weight)
```

```{r}
hist(age)
qqnorm(age)
```

```{r}
hist(zombies_killed)
qqnorm(zombies_killed)
```

```{r}
hist(yrs_edu)
qqnorm(yrs_edu)
```

fix ones that are not normally distributed (zombies killed and yrs of edu) both appear to be right skewed

these are probably poisson because they are integers and idnependantly related 

```{r}
?dpois # dpois gives log density and ppois gives log distribution
zd<-dpois(0:12, lambda = zm)
barplot(zd)
```

```{r}
yd<-dpois(x=0:10, lambda = ym)
barplot(yd)
```

5. Now use the sample() function to sample ONE subset of 30 zombie survivors (without replacement) from this population and calculate the mean and sample standard deviation for each variable. Also estimate the standard error for each variable, and construct the 95% confidence interval for each mean. Note that for the variables that are not drawn from the normal distribution, you may need to base your estimate of the CIs on slightly different code than for the normal.


This is how I subsetted the sample
```{r}
?sample
nd<-d[sample(nrow(d), 30),]
nd
str(nd)
```

mean and standard deviations of samples

```{r}
nheight<-nd$height
nhm<-mean(nheight)
nhm
nhsd<-sd(nheight)
nhsd

nweight<-nd$weight
nwm<-mean(nweight)
nwm
nwsd<-sd(nweight)
nwsd

nage<-nd$age
nam<-mean(nage)
nam
nasd<-sd(nage)
nasd

nzombies_killed<-nd$zombies_killed
nzm<-mean(nzombies_killed)
nzm
nzsd<-sd(nzombies_killed)
nzsd

nyrs_edu<-nd$years_of_education
nym<-mean(nyrs_edu)
nym
nysd<-sd(nyrs_edu)
nysd
```

standard errors and 95% ci

```{r}
hse<-sqrt(nhsd^2/30)
hse

wse<-sqrt(nwsd^2/30)
wse

ase<-sqrt(nasd^2/30)
ase

zse<-sqrt(nzsd^2/30)
zse

yse<-sqrt(nysd^2/30)
yse
```

these are all sample size 30 so t distrubution needs to be used, I am also not sure why the to Poisson distirbutions would have different code for the CI

```{r}
lower <- nhm - qt(1 - 0.05/2, df = 29) * hse  # (1-alpha)/2 each in the upper and lower tails of the distribution
upper <- nhm + qt(1 - 0.05/2, df = 29) * hse  # (1-alpha)/2 each in the upper and lower tails of the distribution
nhci_t <- c(lower, upper)
nhci_t

lower <- nwm - qt(1 - 0.05/2, df = 29) * wse  # (1-alpha)/2 each in the upper and lower tails of the distribution
upper <- nwm + qt(1 - 0.05/2, df = 29) * wse  # (1-alpha)/2 each in the upper and lower tails of the distribution
nwci_t <- c(lower, upper)
nwci_t

lower <- nam - qt(1 - 0.05/2, df = 29) * ase  # (1-alpha)/2 each in the upper and lower tails of the distribution
upper <- nam + qt(1 - 0.05/2, df = 29) * ase  # (1-alpha)/2 each in the upper and lower tails of the distribution
naci_t <- c(lower, upper)
naci_t

lower <- nzm - qt(1 - 0.05/2, df = 29) * zse  # (1-alpha)/2 each in the upper and lower tails of the distribution
upper <- nzm + qt(1 - 0.05/2, df = 29) * zse  # (1-alpha)/2 each in the upper and lower tails of the distribution
zwci_t <- c(lower, upper)
zwci_t

lower <- nym - qt(1 - 0.05/2, df = 29) * yse  # (1-alpha)/2 each in the upper and lower tails of the distribution
upper <- nym + qt(1 - 0.05/2, df = 29) * yse  # (1-alpha)/2 each in the upper and lower tails of the distribution
yaci_t <- c(lower, upper)
yaci_t

```

6. Now draw 99 more random samples of 30 zombie apocalypse survivors, and calculate the mean for each variable for each of these samples. Together with the first sample you drew, you now have a set of 100 means for each variable (each based on 30 observations), which constitutes a sampling distribution for each variable. What are the means and standard deviations of this distribution of means for each variable? How do the standard deviations of means compare to the standard errors estimated in [5]? What do these sampling distributions look like (a graph might help here)? Are they normally distributed? What about for those variables that you concluded were not originally drawn from a normal distribution?


```{r}
library(dplyr)
d1<-tbl_df(d1)
k <- 99 # number of samples
n <- 30 # this has to be 30 because we are sleecting 30 rows
s <- NULL # dummy variable to hold each sample
for (i in 1:k){
    s[[i]] <- sample_n(d1,size=n, replace=FALSE) #we have to use a different function here, using this one that is from the dplyr package allows us t select rows from a tybl of data rather than a vector, this is why we were having problems before, the data we are selecting is not in the form of a vector

}
head(s)# now I have 99 samples of 30 rows with all the variables wooho!

```

Now usign a for loop I will get the means and standard devations of this sample

```{r}
#use a for loop for this...

set.mean.height<-NULL
for (i in 1:99) {
  set.mean.height[i]<-mean(s[[i]]$height)
}
set.mean.height # this is a vector of all the means from all the smaples for heigt

#now lets do this for all the other variables

set.mean.weight<-NULL
for (i in 1:99) {
  set.mean.weight[i]<-mean(s[[i]]$weight)
}
set.mean.weight

set.mean.age<-NULL
for (i in 1:99) {
  set.mean.age[i]<-mean(s[[i]]$age)
}
set.mean.age

set.mean.zombies_killed<-NULL
for (i in 1:99) {
  set.mean.zombies_killed[i]<-mean(s[[i]]$zombies_killed)
}
set.mean.zombies_killed

set.mean.years_of_education<-NULL
for (i in 1:99) {
  set.mean.years_of_education[i]<-mean(s[[i]]$years_of_education)
}
set.mean.years_of_education

```

now lets add the first mean to this sample distirbution 

```{r}

set.mean.height<-append(set.mean.height, nhm) #this worked because now the vector has 100 values, lets do it for the rest

set.mean.weight<-append(set.mean.weight, nwm)
set.mean.age<-append(set.mean.age, nam)
set.mean.zombies_killed<-append(set.mean.zombies_killed, nzm)
set.mean.years_of_education<-append(set.mean.years_of_education, nym)
```

Now that we have the complete set of samples we should find the mean and standard deviation of this.

```{r}

sample_height_mean<-mean(set.mean.height)
sample_height_mean
sample_height_sd<-sd(set.mean.height)
sample_height_sd

#now lets do it for all the variables

sample_weight_mean<-mean(set.mean.weight)
sample_weight_mean
sample_weight_sd<-sd(set.mean.weight)
sample_weight_sd

sample_age_mean<-mean(set.mean.age)
sample_age_mean
sample_age_sd<-sd(set.mean.age)
sample_age_sd

sample_zombies_mean<-mean(set.mean.zombies_killed)
sample_zombies_mean
sample_zombies_sd<-sd(set.mean.zombies_killed)
sample_zombies_sd

sample_edu_mean<-mean(set.mean.years_of_education)
sample_edu_mean
sample_edu_sd<-sd(set.mean.years_of_education)
sample_edu_sd

```

How doe these compare to the one's from before? The means are still very close but the standard devaiations are much smaller now. This is as expected because there are multiple samples, whereas before it was just one sample and looking at the deviation in that one sample. If there are more samples, then the deviation will be smaller because the samples will resemble each other more. It is not a measure of the deivation in one smaple, rather the devaition among all the sample means. 

Finally let's see what they look like. They all look nromal now. The ones that were nto normal before are nromal now since we are looking at a distribution of means among multiple samples. 

```{r}
qqnorm(set.mean.height)
qqnorm(set.mean.weight)
qqnorm(set.mean.age)
qqnorm(set.mean.zombies_killed)
qqnorm(set.mean.years_of_education)
```

