---
title: "ishratc_OriginalHomeworkCode_03"
author: "Ishrat Chowdhury"
date: "October 3, 2019"
output: html_document
---

First let's load our data into R

```{r}
library(curl)
f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN597_Fall19/zombies.csv")
d <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
head(d)
```

1. Calculate the population mean and standard deviation for each quantitative random variable.

```{r}
height<-d$height
hm<-mean(height)
hm
hsd<-sd(height)
hsd

weight<-d$weight
wm<-mean(weight)
wm
wsd<-sd(weight)
wsd

age<-d$age
am<-mean(age)
am
asd<-sd(age)
asd

zombies_killed<-d$zombies_killed
zm<-mean(zombies_killed)
zm
Lambda(zombies_killed)
zsd<-sd(zombies_killed)
zsd

yrs_edu<-d$years_of_education
ym<-mean(yrs_edu)
ym
ysd<-sd(yrs_edu)
ysd

```
2. Use {ggplot} to make boxplots of each of these variables by gender. I guess this can be used for comparison.

```{r}
mh<- d$height[d$gender == "Male"]
fh<- d$height[d$gender == "Female"]
mw<- d$weight[d$gender == "Male"]
fw<- d$weight[d$gender == "Female"]
ma<- d$age[d$gender == "Male"]
fa<- d$age[d$gender == "Female"]
mz<- d$zombies_killed[d$gender == "Male"]
fz<- d$zombies_killed[d$gender == "Female"]
my<- yrs_edu[d$gender == "Male"]
fy<- yrs_edu[d$gender == "Female"]
par(mfrow =c(1,2))
boxplot(mh, main = "Height", xlab = "Males", ylab = "inches")
boxplot(fh, main = "Height", xlab = "Females", ylab = "inches")
boxplot(mw, main = "Weight", xlab = "Males", ylab = "pounds")
boxplot(fw, main = "Weight", xlab = "Females", ylab = "pounds")
boxplot(ma, main = "Age", xlab = "Males", ylab = "years")
boxplot(fa, main = "Age", xlab = "Females", ylab = "years")
boxplot(mz, main = "# of Zombies Killed", xlab = "Males")
boxplot(fz, main = "# of Zombies Killed", xlab = "Females")
boxplot(my, main = "Years of Education", xlab = "Males", ylab = "years")
boxplot(fy, main = "Years of Education", xlab = "Females", ylab = "years")
```

Now to answer the question correctly
```{r}
library(ggplot2)
library(readr)
d1_url<-"https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN597_Fall19/zombies.csv"
d1<-read_csv(d1_url)
head(d1)
```
```{r}
h <- ggplot(d1) +
      geom_boxplot(aes(x=gender, y=height))
h
```

```{r}
w <- ggplot(d1) +
      geom_boxplot(aes(x=gender, y=weight))
w
```

```{r}
a <- ggplot(d1) +
      geom_boxplot(aes(x=gender, y=age))
a
```

```{r}
z <- ggplot(d1) +
      geom_boxplot(aes(x=gender, y=zombies_killed))
z
```

```{r}
y <- ggplot(d1) +
      geom_boxplot(aes(x=gender, y=years_of_education))
y
```

3. Use {ggplot} to make scatterplots of height and weight in relation to age. Are these variables related? Why?

```{r}
hw<- ggplot(d1) + 
      geom_point(aes(x=weight, y=height))
hw
```
q-q plots

```{r}
hist(height)
qqnorm(height)
```

```{r}
hist(weight)
qqnorm(weight)
```

```{r}
hist(age)
qqnorm(age)
```

```{r}
hist(zombies_killed)
qqnorm(zombies_killed)
```


3. Use {ggplot} to make scatterplots of height and weight in relation to age. Are these variables related? Why?

```{r}
hist(yrs_edu)
qqnorm(yrs_edu)
```

fix ones that are not normally distributed (zombies killed and yrs of edu) both appear to be right skewed

actually.. these are probs poisson bc they are integers and idnependantly related 

```{r}
?dpois # dpois gives log density and ppois gives log distribution
zd<-dpois(0:12, lambda = zm)
barplot(zd)
#looks better but there is an outlier (afraid to remove points) also can I transform them 

```

```{r}
yd<-dpois(yrs_edu, lambda = ym)
yd
hist(yd)

yd<-dpois(x=0:10, lambda = ym)
barplot(yd)

#not sur eif either of these make sense
```

the following is just me exploring

found this package that gives a skewness coefficient haha kind of cool not sure if it means anything though

```{r}
install.packages("e1071") 
library(e1071)
sz<-skewness(zombies_killed)
sz
sy<-skewness(yrs_edu)
sy

```

positively skewed data


```{r}
install.packages("outliers")
library(outliers)
outlier(zombies_killed)
```

use sample funcion to sample one subset of 30 zombie suruvivers without replacement, from pop

calc mean and sd for each variable
se for each and 95% ci for each mean
different code for z and y

```{r}
library(dplyr)
sample_n()

?sample
nd<-d[sample(nrow(d), 30),]
nd
```




